### 2018-03-16 manuscript.rmd
added comment about oleocysts

We reconstruct palpons as present in the common ancestor of siphonophores (Fig. 5B), retained in most species, but lost three times independently in the branches leading to Pyrostephidae (represented here by the genera *Bargmannia* and *Rudjakovia*), in calycophorans, and in *Marrus claudanielis* and Undescribed sp. L. Within the calycophorans, one species *Stephanophyes superba* (not included in this phylogeny) has polyp-like zooids that have been described as palpons [@totton1965synopsis], but the exact identity of this zooid is not clear and needs further morphological examination.

>>>>

We reconstruct palpons as present in the common ancestor of siphonophores (Fig. 5B), retained in most species, but lost three times independently in the branches leading to *Bargmannia* and *Rudjakovia* sp., in calycophorans, and in *Marrus claudanielis* and Undescribed sp. L. The pyrostephid *Pyrostephos vanhoeffeni* (not sampled) has modified tentacle-less palpons (termed oleocysts), but the relationship between this species and *Rudjakovia* sp. is not known, so the exact patterns of loss within *Pyrostephidae* remain unclear. Within the calycophorans, one species *Stephanophyes superba* (not included in this phylogeny) has polyp-like zooids that have been described as palpons [@totton1965synopsis], but the exact identity of this zooid is not clear and needs further morphological examination.
